Reviewer #2: Originality: This is a field of growing interest and importance, this work builds on the authors previous publications in this field.  

Title: Ok - I am not sure this is only about embracing complexity - the authors have pushed well beyond that.

Abstract: Fine no comments

Introduction: This will be up to the editor to decide - the introduction is largely philosophical, and quite lengthy with no references for the first several pages.  Many in the industry are already agree about the problems associated with complexity - I am not sure such a long introduction is needed.  As is, we don't really learn what the paper will contribute until Page 4 which is quite late - you may loose many readers by then.    

Literature Review:  Owing to the lengthy introduction, the literature review also appears late.  The present work could do better in terms of integrating itself into the ongoing work in this field which largely supports the author's claim that a simple way of measuring complexity during design is needed.  A few missing references that I am aware of:

Broderick, D., Wright, P., Kattan, R., 2012. Exploring the Link between Structural Complexity and Coating Performance. In: Proceedings of the 11th International Marine Design Conference, vol. 2. pp. 321-337.

Nam et al. Estimation of geometry-based manufacturing cost of complex offshore structures in early design stage Inter J Nav Archit Oc Engng (2012) 4:291-301 http://dx.doi.org/10.2478/IJNAOE-2013-009

Methods/Approach: Fine -clear description, well presented. 

Results: 
What is the meaning of the red in figure 2?  Doesn't seem to fit well on the white-black intensity scale discussed in the text. No data or problem with the model? It will also be hard to decipher when printed in black and white. 

More analysis in this area would be welcome - is it possible to identify specific topologies or features in the high-complexity areas the could be removed?  After 6 pages of lead-up, this was over very quickly!   

Conclusions: If the introduction is going to start so broad, the conclusion should be extended a bit to go back to the high level discussion the paper started with.   What unique conclusions were drawn with regards to the overall complexity problem?  How is the solution unique the shipyard problem etc?  If the introduction is more narrow in the revision, the current conclusion is fine.

Language: No issues

Ethical Issues: No issues

Add complexity of submairne and reference